\papertitle

### 2020-02-07 paper/paper-old.tex

Based on their needs, the climate and weather community has developed a software ecosystem that supports them to execute their large-scale workflows.
While the current advances correspond to a big leap forward, many processes still require experts.
For example, porting a workflow from one system to another requires to adjust runtime parameters of applications and to decide how data is managed.
Since performance is of crucial importance to large-scale workflows, careful attention must be paid to exploit the system characteristics of the target supercomputer.
To obtain the best performance, a specific supercomputer typically requires substantial changes to the workflow to tailor the workflow to the particular machine.
For instance, a data-driven workflow may benefit from using a heterogeneous set of computing and storage technology at the same time.

@@

  \item \textbf{Cylc}
  %Cylc parses the suite file, generate dependencies and defines a schedule for the execution.
  Now, Cylc calls EIOS to identify potential optimisations in the schedule.
  EIOS may decide that subsequent jobs shall be placed on the same node or to reorder the execution of some jobs.
  Also, it may provide information for conducting data migration.

@@

  \item \textbf{Slurm}
  %Schedules the execution of the job considering the scheduling policy of the data centre.
  Cylc may now have added a constraint to place a job on the same node as a previous job and that is now handled by a modified Slurm.
  Also, if migrations have to be performed before or after a job, Slurm will administer them.

  \item \textbf{Job}
  A job might be scheduled on the same nodes than a previous job to utilize local storage.
  %The user-provided script is executed on a single node assigned to the job.
  % The script has set environment variables containing information about the Cylc execution (e.g., a task in the workflow) and the Slurm job (e.g., number of nodes).

  \item \textbf{Script}
  %The shell-script executes the sequence of commands.
  % Typically, to create a filename, the script calls Cylc commands with a template provided by the user and feeds this information to the application.
  % This ultimately defines the storage location to be used.
  % A script typically consists of multiple fine-grained commands and may even call multiple parallel applications.
  The way the filenames are generated is now different. A replacement command invokes EIOS to generate a pseudo filename.
  This filename will encode additional information for ESDM about how to prioritise data placement according to data access.
  Potentially, EIOS may generate an \texttt{esdm.conf} file for the specific application to adjust the mapping of data to available storage targets.

  \item \textbf{Application}
  %The user-specified parallel application runs.
  The application may either use NetCDF with ESDM support or ESDM directly to access datasets.
  Hence, in \Cref{fig:layers}, the HDF5 layer is replaced with ESDM.
  ESDM loads the \texttt{esdm.conf} file that contains the information about the available storage backends and their configuration.
  % Knowing the potential targets, ESDM schedules application-local I/O.
  ESDM extracts the long-term schedule information from the generated filenames and considers it during the I/O scheduling to exploit the data locality between tasks.

>>>>

Based on their needs, the HPC community has developed a software ecosystem that supports them to execute their large-scale workflows.
While the current advances correspond to a big leap forward, many processes still require experts.
For example, porting a workflow from one system to another requires to adjust runtime parameters of applications and to decide how data is managed.
Since performance is of crucial importance to large-scale workflows, careful attention must be paid to exploit the system characteristics of the target supercomputer.
To obtain the best performance, a specific supercomputer typically requires substantial changes to the workflow to tailor the workflow to the particular machine.
For instance, a data-driven workflow may benefit from using a heterogeneous set of computing and storage technology at the same time.

@@

  \item \textbf{Cylc}
  Now, Cylc calls EIOS to identify potential optimisations in the schedule.
  EIOS may decide that subsequent jobs shall be placed on the same node or to reorder the execution of some jobs.
  Also, it may provide information for conducting data migration.

@@

  \item \textbf{Slurm}
  Cylc may now have added a constraint to place a job on the same node as a previous job and that is now handled by a modified Slurm.
  Also, if migrations have to be performed before or after a job, Slurm will administer them.

  \item \textbf{Job}
  A job might be scheduled on the same nodes than a previous job to utilize local storage.

  \item \textbf{Script}
  The way the filenames are generated is now different. A replacement command invokes EIOS to generate a pseudo filename.
  This filename will encode additional information for ESDM about how to prioritise data placement according to data access.
  Potentially, EIOS may generate an \texttt{esdm.conf} file for the specific application to adjust the mapping of data to available storage targets.

  \item \textbf{Application}
  The application may either use NetCDF with ESDM support or ESDM directly to access datasets.
  Hence, in \Cref{fig:layers}, the HDF5 layer is replaced with ESDM.
  ESDM loads the \texttt{esdm.conf} file that contains the information about the available storage backends and their configuration.
  ESDM extracts the long-term schedule information from the generated filenames and considers it during the I/O scheduling to exploit the data locality between tasks.
